### 2023-09-02 2.State/lstm.tex
Finished all lstm variants

>>>>

\subsubsection{Other small variants}

\begin{itemize}
  \item Removing the activation function from the Vanilla \ac{LSTM} for :
    \begin{itemize}
      \item the candidate cell and thus becomes $ \tilde{c}_t=(w_c\cdot[x_{t-1},h_{t-1}] + b_c) $, this is called the \ac{NIAF}
      \item the output of the previous cell state and thus becomes $ h_t=o_t\cdot c_t $, and is called \ac{NOAF}
    \end{itemize}
  \item Using units instead of the respective gates :
    \begin{itemize}
      \item \ac{NIG} : $i_t=1$
      \item \ac{NOG} : $o_t=1$
      \item \ac{NFG} : $f_t=1$
    \end{itemize}
\end{itemize}
